---
title: "Assignment 3"
author: "Oguzhan Dilber"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}

set.seed(2017556019)
library(tidyverse)
library(dplyr)
library(knitr)

```

## 1. Write a function that finds a prime number(s) given a set of numbers. For example you have a vector of numbers like (89, 107, 597, 931, 1083). The function you will write should return a logical vector depending on the given number is prime or not.

```{r}
input<-c(5,17,13,32,11,3,103,7,10)

is_prime <- function(n){
  if(n == 0) {
    FALSE
  }
  else if(sum(n %% (1:n) == 0) > 2){
    FALSE
  }
  else{
    TRUE
  }
}

result <- sapply(input,is_prime)
```
 
5,17,13,32,11,3,103,7,10 is in order of ->`r result`


## 2.Write a function that finds the letter numbers of all words in a given text and sorts the text according to those numbers from words with few letters to words with many letters. Sort the words containing the same number of letters alphabetically.

```{r include=FALSE}
mysentences<-sample(sentences,5,)
```

```{r}


convert_func <- function(n){

rmv<-str_c(n,sep = ".",collapse = " ")

nodot<-str_replace_all(rmv,"\\.","")

newdata <- nodot %>%
  str_split(" ",simplify = FALSE)

newdata<-sort(newdata[[1]])

newvector<-c()

for (i in 1:length(newdata)) {
newvector[i]<-str_length(newdata[i])
}

mydata<- tibble(
  word = newdata,
  num = newvector,
)

mytable<-mydata %>% 
  group_by(word) %>%
  arrange(num)

myvec<-c()

myvec<-mytable$word

lastvec<-c()
lastvec<-myvec %>% str_c(collapse = " ")
lastvec
}

```
Sort the words alphabetically and numbers

`r convert_func(mysentences)`




