---
title: "Assignment 2-Part2"
author: "Oguzhan Dilber"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}
set.seed(2017556019)
library(tidyverse)
library(knitr)
words<-stringr::words
```

## 1.Take a sample of 100 words from this data, and save this sample as a new data
  
```{r echo=FALSE}
newdataset <- sample(words,100)
kable(newdataset)
```

## 2.Find words which are starting with “a” and ending with “e”.
```{r include=FALSE}
starta <- str_subset(newdataset,"^a")
ende <- str_subset(starta,"e$")
if (length(ende)==0) {
 ende<- print("There are no match")
}
ende
```
Words are starting with “a” and ending with “e” : `r ende`

## 3.Calculate the number of words which have more than 3 vowels.

```{r echo=FALSE}
sumdata<-sum( str_count(newdataset, "[aeiou]") >3)

```
Number of words which have more than 3 vowels is `r sumdata`.

## 4.List the five longest word in your data

```{r echo=FALSE}
df <-str_length(newdataset)

mydata<- tibble(
   word = newdataset,
   length = df,
 )

mylist<- mydata %>%
   group_by(word) %>%
   arrange(desc(length)) %>%
   head(5)
kable(mylist)
```

## 5.Try to find word(s) which contain any of these words: age, any, day, exp, her, pro, the.

```{r echo=FALSE}
find<-c("age","any","day","exp","her","pro")
find_match<-str_c(find,collapse = "|")
has_find<-str_subset(newdataset,find_match)
matches<-str_extract(has_find,find_match)
result<-head(has_find)
```
Words containing these: `r result`
